---
title: "The Heliotronics Case"
author: 'Team 2: Elena Pshenichnikova & Lina Simonian'
date: "2025-03-13"
output: html_document
---

```{r, include=FALSE}
# Load required libraries
library(ggplot2)
library(dplyr)
library(readr)
library(broom)
library(lm.beta)
library(ggplot2)

#Readability in HTML report
#install.packages("DT")
library(DT)

# clear the database
rm(list=ls()) 

# Reading the data
url <- "https://raw.githubusercontent.com/pshenic4/Advanced-Data-Driven-Decision-Making/becf907b2c87751501daf026ad531a7767f38081/Case_Stud_%20I.csv"
Data <- read_csv(url)
```

<div style="border: 2px solid #007acc; padding: 10px; border-radius: 5px;">
## Question 1

Use an electronic spreadsheet to plot the data displayed in the table and draw a scatter plot (point diagram).  

Does the **multiplicative learning model** which assumes the following relationship:  

\[
Y = A X^b
\]

apply to this data set?  

In our case **Y** are the average manufacturing cost of the last batch of 100 solar panels at Heliotronic in $ after having produced a cumulative production of **X** solar panels.  

In the table **X** represents the column labeled **total number of solar panels produced** at Heliotronics.  

**b** is the **experience parameter** not to be confused with the learning rate.  

**A** is the price or **cost of the first unit**.  

Obviously, \[ Y = A X^b \] is **not a linear relationship** of the type that regression analysis can model (**y = a + b₁x₁**).  

So the question now is to **transform the data in order to get a linear relationship**.  

Make an appropriate transformation of the data and redo the plot with the transformed data.
</div>

```{r}
# Step 1
## Plotting the data
## `geom_smooth()` using method = 'loess' and formula = 'y ~ x'
ggplot(Data, aes(x = number_of_solar_panels, y = manufacturing_cost)) +
  geom_point(color = 'blue') +
  geom_smooth(color = 'black')+
  labs(title = "Scatter Plot of Production vs. Manufacturing Cost", 
       x = "Total Production (Solar Panels)", 
       y = "Manufacturing Cost per Unit ($)") +
  theme_minimal()
```



```{r}
# Step 2
## Logarithm transformation

Data=Data %>% mutate(Log_number_of_solar_panels=log(number_of_solar_panels))
Data=Data%>% mutate(Log_manufacturing_cost=log(manufacturing_cost))
datatable(Data, options = list(scrollX = TRUE))
```

```{r}
# Step 3
## Plotting transformed data
ggplot(Data, aes(x = Log_number_of_solar_panels, y = Log_manufacturing_cost)) +
  geom_point(color = 'red') +
  geom_smooth(method = "lm", color = 'black', se = FALSE) +
  labs(title = "Log-Log Scatter Plot of Production vs. Cost with Fitted Curve", 
       x = "Log of Total Production", 
       y = "Log of Manufacturing Cost") +
  theme_minimal()
```

By taking the natural logarithm of both sides we converted the power-law function into a linear relationship. 

<div style="border: 2px solid #007acc; padding: 10px; border-radius: 5px;">
## Question 2

Once you have answered the above questions, **conduct a linear regression with the transformed data**:  
**Use R** to estimate the **regression model**.  

Please **interpret the results of the regression analysis**!  How well does the model explain the data?  

What is the **learning rate** that applies in this case?
</div>

```{r}
# Fit the log-log regression model
model <- with(Data, lm(Log_manufacturing_cost ~ Log_number_of_solar_panels))

# Display the summary of the model
summary(lm.beta(model))
```

This regression model estimates the relationship between **log-transformed manufacturing cost** and **log-transformed number of solar panels produced** to determine whether the **multiplicative learning model** applies.

---

#### **Model Equation**
The estimated regression equation is:

\[
\log(\text{Manufacturing Cost}) = 7.8503 - 0.155 \times \log(\text{Number of Solar Panels})
\]

- **Intercept (7.8503)** → Represents **log(A)**, where **A** is the estimated cost of the **first solar panel**.  
  - Taking the exponential:  
    \[
    A = e^{7.8503} \approx 2555.12 
    \]
    This suggests that **when one solar panel is produced, the estimated cost per unit is ~$2555.12**.

- **Slope (-0.155)** → This is the **experience parameter (b_1)**.
  - A **negative value** confirms that **costs decrease as production increases** (**economies of scale**).
  - Specifically, for **every 1% increase in production**, the **manufacturing cost per unit decreases by 0.155%**.

---

#### **Model Fit: How Well Does the Model Explain the Data?**

| Metric | Value | Interpretation |
|---------|-------|----------------|
| **Multiple R²** | **0.9502** | The model explains **95.02% of the variation** in manufacturing cost. |
| **Adjusted R²** | **0.9477** | Very close to R², meaning the model is strong even after adjusting for complexity. |
| **F-statistic** | **381.4** | Very high value, confirming the model is statistically significant. |
| **p-value** | **1.701e-14 (< 0.001)** | The model is highly significant, meaning there is a strong relationship between production and cost. |
| **Residual Standard Error** | **0.0299** | Small residual error, indicating accurate predictions. |

 **Conclusion:**  
- The model **fits the data  well**.
- **95% of the cost variation** is explained by production volume.
- The **negative slope confirms cost reduction with increased production**.

---

#### **Learning Rate (LR) Calculation**

**Computing Log of Cost at** \( X \)
\[
\log(Y_x) = b_0 + b_1 \cdot \log(X)
\]
```{r}
#Step 1
# Extract the maximum X (log scale)
X_log <- max(Data$Log_number_of_solar_panels)  # Using max log-transformed production level

# Compute log(Yx) using the regression model
log_Yx <- 7.8503 + (-0.154991 * X_log)  # Using  log-transformed X 
Yx <- exp(log_Yx)  # Convert back from log(Y) to actual cost
```

```{r, echo = FALSE}
# Print results
cat("Production Level (Log_X):", X_log, "\n")
cat("Manufacturing Cost at X accordingly to the model:", round(Yx, 2), "\n")
```

**Computing Log of Cost at \( 2X \) **
\[
\log(Y_2x) = b_0 + b_1 \cdot \log(2X)
\]
```{r}
#Step 2
# Define regression coefficients
b0 <- 7.8503  # Intercept
b1 <- -0.154991  # Slope

# Compute log(Y2x) for doubled production (2X)
X2_log <- X_log + log(2)  # Since log(2X) = log(X) + log(2)
log_Y2x <- b0 + (b1 * X2_log)
Y2x <- exp(log_Y2x)  # Convert back from log(Y) to actual cost
```

```{r, echo = FALSE}
# Print results
cat("Doubled Production Level (Log_2X):", X2_log, "\n")
cat("Manufacturing Cost at 2X accordingly to the model:", round(Y2x, 2), "\n")
```

**Computing Learning Rate (LR)**
The learning rate formula is:
\[
LR = 1 - \frac{Y_{2X}}{Y_X}
\]

```{r}
#Step 3
# Compute Learning Rate (LR)
learning_rate <- 1 - (Y2x / Yx)
```

```{r, echo = FALSE}
# Print learning rate
cat("Estimated Learning Rate (LR):", round(learning_rate * 100, 2), "%\n")
```

**Interpretation:**
- Learning Rate (LR) = 10.19%
- This means that when production doubles from 2200 to 4400 units, the manufacturing cost per unit decreases by 10.19%.

<div style="border: 2px solid #007acc; padding: 10px; border-radius: 5px;">
## **Question 3**

Please **use the experience curve** estimate from the regression model to calculate the expected **average manufacturing cost per solar panel for the 400 solar panels** that would be produced for Switzerland.  

**Hint**: estimate the average production cost per solar panel for **4700, 4800, 4900 and 5000 units and compute their mean**.
</div>

Predict Costs for 4700, 4800, 4900, and 5000 Units:
```{r}
#Step 1
# Define production levels for prediction
production_values <- c(4700, 4800, 4900, 5000)

# Compute predicted log cost
log_predicted_costs <- b0 + b1 * log(production_values)  # Natural log used

# Convert back from log cost to actual cost ($)
predicted_costs <- exp(log_predicted_costs)

# Print predicted costs
df <- data.frame(number_of_solar_panels = production_values, manufacturing_cost = round(predicted_costs, 2))
datatable(df, options = list(scrollX = TRUE, pageLength = 5))
```

- Calculate the expected average manufacturing cost per solar panel for the 400 solar panels:

```{r}
#Step 2
# Compute the mean predicted cost
avg_cost <- mean(predicted_costs)
```

```{r, echo = FALSE}
# Print final predicted bid
cat("Average Manufacturing Cost per Solar Panel: $", round(avg_cost, 2), "\n")
```

<div style="border: 2px solid #007acc; padding: 10px; border-radius: 5px;">
## **Question 4**

Please **calculate a 95% confidence interval for the average manufacturing cost per solar panel** for the panels produced for Switzerland by using the lower and upper bounds of the confidence interval estimate for the experience parameter.  

You should calculate **two extra regression equations** for both limits and then calculate the expected **average manufacturing cost per solar panel** for the **400 solar panels** that would be produced for Switzerland as in exercise 3.
</div>

Extracting 95% Confidence Interval for the Experience Parameter:
```{r}
#Step 1
# Extract the 95% confidence interval for the slope (b1)
conf_int <- confint(model)

# Lower and Upper Bound for experience parameter (b1)

b0_LB <- conf_int[1, 1]
b0_UB <- conf_int[1, 2]
b1_LB <- conf_int[2, 1]
b1_UB <- conf_int[2, 2]
```


Apply Confidence Interval Bounds:
```{r}
#Step 2
# Compute log costs using the confidence interval bounds (without repeating predictions)
log_cost_LB <-  b0_LB + b1_LB * log(production_values)
log_cost_UB <- b0_UB + b1_UB * log(production_values)

# Convert back to actual cost ($)
cost_LB <- exp(log_cost_LB)
cost_UB <- exp(log_cost_UB)

# Store results in a data frame
predicted_costs_CI <- data.frame(
  number_of_solar_panels = production_values, 
  manufacturing_cost_LB = round(cost_LB, 2),
  manufacturing_cost_UB = round(cost_UB, 2)
)

# Display results
predicted_costs_CI
```

Compute the Average Cost for LB and UB:
```{r}
#Step 3
# Compute the mean predicted cost for LB and UB
mean_cost_LB <- mean(cost_LB)
mean_cost_UB <- mean(cost_UB)
```

```{r, echo = FALSE}
# Print final confidence interval results
cat("95% Confidence Interval for Average Manufacturing Cost per Solar Panel:\n")
cat("Lower Bound (LB): $", round(mean_cost_LB, 2), "\n")
cat("Upper Bound (UB): $", round(mean_cost_UB, 2), "\n")
```

## **Conclusion: Estimating Productivity Gains for Heliotronics' Swiss Bid**

Based on our **experience curve analysis**, we estimate the **expected manufacturing cost reduction** for Heliotronics as they scale production before producing **400 solar panels for the Swiss canton of Tessin**.

### **Experience Curve Validation**  
The **log-log transformation produced a linear relationship**, confirming that Heliotronics' **manufacturing cost reductions follow a power-law experience curve**.  
The estimated **learning rate (~10.19%)** indicates that **cost per panel decreases by approximately 10% every time cumulative production doubles**.

### **Cost Projection for Switzerland (400 Panels in April 2022)**  
Heliotronics will have produced **2,400 additional solar panels before starting production for Switzerland**.  
Using the **experience curve model**, we estimated the expected **average cost per solar panel** at that stage.  
The **predicted cost was computed using cumulative production levels (4700–5000 panels)**, providing a **data-driven estimate for competitive bidding**.

## **Conclusion: Estimating Cost & Bid Strategy for Switzerland**

Our analysis confirms that **Heliotronics' manufacturing cost follows an experience curve**, with an estimated **learning rate of ~10.19%**. This means that **each time cumulative production doubles, per-unit costs decrease by approximately 10%**.

### **Projected Cost for the Swiss Bid**
**By the time Heliotronics produces the 400 solar panels for Switzerland, total production will have increased by 2,400 units.**  
**Based on the experience curve model, the estimated manufacturing cost per panel falls within the following range:**  

  **95% Confidence Interval for Cost per Solar Panel: [$598.54 - $792.72]**  

### **Recommended Bid Strategy**
 **A bid closer to $534.33 would maximize competitiveness**, making Heliotronics a strong contender in the Swiss market.  
 **A bid near $888.02 provides a buffer against cost uncertainties**, ensuring sustainable profit margins.  
 **Strategic Recommendation:** To balance **competitiveness and profitability**, **Heliotronics should place a bid between $534.33 and $888.02**, considering market conditions and pricing strategy.




